HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-04-27 docs/HLL_exp_bad/main.tex
adding comment on expts

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in the Section 5.1 of \cite{hllvuln}. In that paper, the authors target the Redis~\cite{redishll} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5.

>>>>

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in Section 5.1 of~\cite{hllvuln}. In that paper, the authors target the Redis~\cite{redishll} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5. \kenny{I think we can say more here -- isn't it true that the attack in Section 5.1 of~\cite{hllvuln} is in the M2 scenario? Which is our S1? Whereas the attack you describe here is more like an S2 attack, a much weaker attack model?}
